On the analytic structure of the linear response susceptibility in open systems

### 2018-04-12 AnalyticStructure_main.tex
update

The analysis is based on the spectral decomposition of the Liouville equation \eqref{LiouvillianRhopomegaDef1} and the make usage of the \emph{excitation operators}, defined through the 
operator eigenvalue equation
\be\lb{ExcitationOperatorsDef1}
\Liouv \op E = E \op E \;, %\qq \op{\tilde E} \Liouv = E \op{\tilde E}
\ee
with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$.
%\be
%\trace{\op E\op E'} = \delta(E-E') \;. \nn
%\ee
The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. 
This condition allows us to introduce a dyadic representation of excitations as follows
\be\lb{ExcitationOperatorsDef2}
\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, 
\ee
where the \emph{excited states} $\ket{\phi^E_p}$ and $\bra{\chi^E_p}$ span the domain of $\op Q_0$, \emph{i.e} the empty subspace of $\hnot$. The eigenvalue condition \eqref{ExcitationOperatorsDef1} 
can thus be recasted in the form of a Sternheimer-like equations for the excited states
\begin{align}
\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= E \ket{\phi_p^E} \;, \\
\bra{\chi_p^E}\left(\hnot - \eps_p\right) + \bra{\psi_p}\op V'[\op E]\op Q_0   &= -\bra{\chi_p^E} E  \;, \nn
\end{align}
and the orthonormalization condition of the excitation operators is expressed as 
\be
\sum_p \left(\braket{\phi_p^E | \phi_p^{E'}} + \braket{\chi_p^E | \chi_p^{E'}}\right) = \delta(E-E') \;. \nn
\ee

>>>>

The analysis is based on the spectral decomposition of the Liouville equation \eqref{LiouvillianRhopomegaDef1} and the make usage of the \emph{excitation operators}, defined through the 
operator eigenvalue equation
\be\lb{ExcitationOperatorsDef1}
\Liouv \op E = E \op E \;, %\qq \op{\tilde E} \Liouv = E \op{\tilde E}
\ee
with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$ (WRONG!!!).
%\be
%\trace{\op E\op E'} = \delta(E-E') \;. \nn
%\ee
The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. 
This condition allows us to introduce a dyadic representation of excitations as follows
\be\lb{ExcitationOperatorsDef2}
\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, 
\ee
where the \emph{excited states} $\ket{\phi^E_p}$ and $\bra{\chi^E_p}$ span the domain of $\op Q_0$, \emph{i.e} the empty subspace of $\hnot$. The eigenvalue condition \eqref{ExcitationOperatorsDef1} 
can thus be recasted in the form of a Sternheimer-like equations for the excited states
\begin{align}
\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= E \ket{\phi_p^E} \;, \\
\bra{\chi_p^E}\left(\hnot - \eps_p\right) + \bra{\psi_p}\op V'[\op E]\op Q_0   &= -\bra{\chi_p^E} E  \;, \nn
\end{align}
and the orthonormalization condition of the excitation operators is expressed as 
\be
\sum_p \left(\braket{\phi_p^E | \phi_p^{E'}} + \braket{\chi_p^E | \chi_p^{E'}}\right) = \delta(E-E') \;. \nn
\ee

\vspace{0.3cm}
\noindent{TODO: Identify the more convenient equations to present the localization argument on the excited states. 
\vspace{0.3cm}

Due to the previous argument we can state that the localization feature of the excited states depend on the energy of the excitation to which they belong. In particular if $E<\eps_p$ the
state $\ket{\phi^E_p}$ behaves as a bound-state

%defined in the dyadic representation of the excitation operators possess  that 
%state that the excitation spectrum is
